---
title: "Create Chapter-Level Codebook from responses.csv"
output: html_notebook
---
Make a chapter-level-codebook from responses.csv that will do the following:  
- Create a "chapter_codebook" with the count of pages within each chapter.
This assumes we start with a basic `responses.csv` file.

In this data processing, we will treat student_id+class_id+release as a unique student. If a student responds in two release versions (e.g., 4.2 and 5.0), that student will appear as two cases.
```{r}
#### Import Data and Setup
library(mosaic)
library(dplyr)
library(tidyverse)
library(ggplot2)
```

```{r}
responses <-read.csv("responses.csv")
responses_all <- responses
codebook_page_final <- read.csv("codebook_page_final.csv")
```


# create chapter codebook with number of pages
```{r}
codebook_chapter <-codebook_page_final %>%
  group_by(chapter_num, book, release) %>%
  mutate(num_pages = n()) %>%
  select(chapter_num, book, release, num_pages) %>%
  distinct()
```


```{r}
write.csv(codebook_chapter, "codebook_chapter.csv")
```

