---
title: Create Page-Level Codebook from `page_views.Rdata`
output: html_notebook
---

The purpose of this script is to make a page-level codebook (eventually called `codebook_page`) from `page_views.Rdata` that will do the following: 

In `page_views`, `page` variable is a string that includes both the chapter and page number (e.g., 10.4 represents chapter 10, page 4) and descriptive text. This codebook will have variables called `chapter_num` and `page_num` that each only include one number (e.g., `chapter_num` will be 10 and `page_num` will be 4).


## Set up and load `page_views.Rdata`

```{r}
# load libraries
library(mosaic)
library(dplyr)
library(tidyverse)
library(ggplot2)

# start with raw data from page_views.Rdata
setwd("~/Desktop/github repository/data/2023-college/raw")
load("page_views.Rdata")
classes <-read.csv("classes.csv")

# there should be no duplicates but just in case, this removes duplicate rows
page_views_all <- distinct(page_views)
```


```{r}
#leftjoin page_views and class_id to get book and release
page_views_class <- page_views %>%
  left_join(classes, by=c("class_id"))

page_views <- page_views_class
```


## Create page_num and chapter_num variables

```{r}
# make a data frame where each row is a page
codebook_page <- page_views %>%
  select(release, book,chapter, page) %>%
  unique() %>%
  mutate(chapter_num = as.numeric(gsub("\\D", "", chapter)),
         page_string = str_extract(str_trunc(page, 8, "right"), "\\d+\\.*\\d*"),
         page_num_from_string = as.numeric(str_extract(str_trunc(page, 8, "right"), "\\d+\\.*\\d*")),
         temp_page_within_ch = round((page_num_from_string - chapter_num)/10,3),
         is_10 = grepl(".10", page_string, fixed = TRUE),
         is_between_10_20 = temp_page_within_ch > .010 & temp_page_within_ch < .019,
         page_within_ch = ifelse(is_10 | is_between_10_20, temp_page_within_ch*10, temp_page_within_ch)) %>%
  select(release, book, chapter, page, chapter_num, page_within_ch) %>% 
  mutate(page_num = page_within_ch*100) %>%
  select(-page_within_ch) %>%
  filter(!is.na(page_num))

```


```{r}
#save codebook
setwd("~/Desktop/github repository/data/2023-college/codebooks")
write.csv(codebook_page, "codebook_page_pageviews.csv")
```
