---
title: "Learnosity Exercises (non-coding questions)"
output: html_notebook
---

The purpose of this script is to produce two data files:

1. `student_page_lrn.RData`
  - each row is a unique `student_id`+`class_id`+`chapter_num`+`page_num`
  - note that each class only uses one `book` with a particular `release`
2. `student_ch_lrn.RData`
  - each row is a unique combination of `student_id`+`class_id`+`chapter_num`
  
These data files include learnosity question metrics such as: 
- correctness on auto-scored questions (n as well as proportion)
- completeness/submits on all learnosity question types (n as well as proportion)
- note that, unlike coding exercises, learnosity questions can only be submitted once (students receive feedback on auto-scored items immediately afterwards) so each student can only have a max of one attempt per question

## Set up

```{r}
# load relevant libraries
library(tidyverse)
library(mosaic)

# start with raw data from responses.Rdata
load("../raw/responses.Rdata")
responses_all <- responses 

# load all codebooks
codebook_all_surveys <- read.csv("../codebooks/codebook_all_surveys.csv")
codebook_page <- read.csv("../codebooks/codebook_page.csv")
codebook_chapter <- read.csv("../codebooks/codebook_chapter.csv")
```

## Create temporary files: responses from all learnosity items and responses from auto-graded learnosity items

Define which are the auto-graded questions.
```{r}
lrn_types <- c("mcq", "choicematrix", "shorttext", "plaintext", "clozeassociation", "association","imageclozeassociation", "sortlist","formulaV2")

lrn_types_auto <- c("mcq", "clozeassociation", "association","imageclozeassociation",
  "sortlist","formulaV2")

```

- Merge variables `page_num` and `chapter_num` into `responses`. 
- Filter out any survey responses.
- Filter for learnosity responses only.
- Filter for auto-graded learnosity responses only.

```{r}
responses_lrn <- responses %>%
  left_join(codebook_page, by=c("book", "release", "chapter", "page")) %>%
  select(book,release, class_id, student_id, chapter_num, page_num, 
         item_id, item_type, completes_page, response,
         points_possible, points_earned, attempt, 
         lrn_question_reference, lrn_type) %>%
  filter(!(item_id %in% codebook_all_surveys$item_id)) %>%
  filter(!(is.na(page_num))) %>%
  filter(item_type != "code") 

responses_auto <- responses_lrn %>%
  filter(lrn_type %in% lrn_types_auto) 
```


## 1. Create `student_page_lrn.RData`

### 1.1. Create variables related to auto-scored questions 

Temporary data frame: `student_page_auto`

Variables included:
- `n_correct_auto_pg` per page, how many auto-scored questions answered correctly
- `n_submit_auto_pg` per page, number of auto-scored questions answered/submitted at all (this number is equal to or less than total number of auto-scored questions on the page)
- `prop_correct_auto_pg` per page, proportion of auto-scored questions answered correctly out of total auto-scored questions (should not be greater than 1)
- `prop_submit_auto_pg` per page, proportion of auto-scored  questions submitted out of total auto-scored questions (should not be greater than 1)

```{r}

student_page_auto <- responses_auto %>%
  group_by(book, release, class_id, student_id, chapter_num, page_num) %>%
  mutate(n_correct_auto_pg = sum(points_earned, na.rm=TRUE),
         n_submit_auto_pg = sum(attempt, na.rm=TRUE)) %>% 
  left_join(codebook_page, by=c("book", "release", "chapter_num", "page_num")) %>%
  select(book, release, class_id, student_id, chapter_num, page_num, 
         n_correct_auto_pg, n_submit_auto_pg, n_lrn_q, lrn_auto) %>%
  mutate(prop_correct_auto_pg = n_correct_auto_pg / lrn_auto,
         prop_submit_auto_pg = n_submit_auto_pg / lrn_auto) %>%
  distinct() %>%
  select(-n_lrn_q, -lrn_auto)

```

Sanity check, the proportion variables should not be greater than 1.

```{r}
favstats(~ prop_correct_auto_pg, data = student_page_auto)
favstats(~ prop_submit_auto_pg, data = student_page_auto)

```

### 1.2. Create variables related to submits on all learnosity questions

Temporary data frame: `student_page_submit`

Variables included:
- `n_submit_pg` per page, how many questions answered/submitted at all (this number is equal to or less than total number of questions on the page)
- `prop_submit_pg` per page, proportion of learnosity questions submitted out of total learnosity questions (should not be greater than 1)

```{r}

student_page_submit <- responses_lrn %>%
  group_by(book, release, class_id, student_id, chapter_num, page_num) %>%
  mutate(n_submit_pg = sum(attempt, na.rm=TRUE)) %>% 
  left_join(codebook_page, by=c("book", "release", "chapter_num", "page_num")) %>%
  select(book, release, class_id, student_id, chapter_num, page_num, n_submit_pg, n_lrn_q) %>%
  mutate(prop_submit_pg = n_submit_pg / n_lrn_q) %>%
  select(-n_lrn_q) %>%
  distinct()

```

Sanity check, the proportion variables should not be greater than 1.

```{r}
favstats(~ prop_submit_pg, data = student_page_submit)
```

### 1.3. Create variables related to completion on all learnosity types

Temporary data frame: `student_page_type`

Variables included:
- `n_submit_pg_[lrntype]` per page, how many of each lrntype answered/submitted at all

```{r}

student_page_type <- responses_lrn %>%
  group_by(book, release, class_id, student_id, chapter_num, page_num, lrn_type) %>%
  mutate(n_submit_pg = sum(attempt, na.rm=TRUE)) %>% 
  select(book, release, class_id, student_id, chapter_num, page_num, lrn_type, n_submit_pg) %>%
  distinct() %>%
  pivot_wider(names_from = lrn_type, 
              names_glue = "n_submit_pg_{lrn_type}",
              values_from = n_submit_pg) %>%
  distinct()

```

### 1.4. Put three page level data together

```{r}

student_page_lrn <- student_page_submit %>%
  left_join(student_page_auto, by=c("book", "release", "class_id", "student_id", "chapter_num", "page_num")) %>%
  left_join(student_page_type, by=c("book", "release", "class_id", "student_id", "chapter_num", "page_num"))

```

```{r}

#save(student_page_lrn, file = "../level-page/student_page_lrn.Rdata", compress = "xz", compression_level = 9)

```

## 2. Create `student_ch_lrn.RData`

### Create variables related to auto-scored questions 

Variables included:
- `n_submit_ch` per chapter, how many questions answered/submitted at all (this number is equal to or less than total number of questions on the chapter)
- `n_correct_auto_ch` per chapter, how many auto-scored questions answered correctly
- `n_submit_auto_ch` per chapter, number of auto-scored questions answered/submitted at all (this number is equal to or less than total number of auto-scored questions on the chapter)
- `n_submit_ch_[lrntype]` per chapter, how many of each lrntype answered/submitted at all
- `prop_submit_pg` per chapter, proportion of learnosity questions submitted out of total auto-scored questions (should not be greater than 1)
- `prop_correct_auto_ch` per chapter, proportion of auto-scored questions answered correctly out of total auto-scored questions (should not be greater than 1)
- `prop_submit_auto_ch` per chapter, proportion of auto-scored questions submitted out of total auto-scored questions (should not be greater than 1)


```{r}

student_ch_lrn <- student_page_lrn %>%
  group_by(book, release, class_id, student_id, chapter_num) %>%
  mutate(n_submit_ch = sum(n_submit_pg, na.rm=TRUE),
         n_correct_auto_ch = sum(n_correct_auto_pg, na.rm=TRUE),
         n_submit_auto_ch = sum(n_submit_auto_pg, na.rm=TRUE),
         n_submit_ch_plaintext = sum(n_submit_pg_plaintext, na.rm=TRUE),
         n_submit_ch_mcq = sum(n_submit_pg_mcq, na.rm=TRUE),
         n_submit_ch_choicematrix = sum(n_submit_pg_choicematrix, na.rm=TRUE),
         n_submit_ch_shorttext = sum(n_submit_pg_shorttext, na.rm=TRUE),
         n_submit_ch_clozeassociation = sum(n_submit_pg_clozeassociation, na.rm=TRUE),
         n_submit_ch_association = sum(n_submit_pg_association, na.rm=TRUE),
         n_submit_ch_imageclozeassociation = sum(n_submit_pg_imageclozeassociation, na.rm=TRUE),
         n_submit_ch_sortlist = sum(n_submit_pg_sortlist, na.rm=TRUE),
         n_submit_ch_formulaV2 = sum(n_submit_pg_formulaV2, na.rm=TRUE)
         ) %>%
  left_join(codebook_chapter, by = c("book", "release", "chapter_num")) %>%
  mutate(prop_submit_ch = n_submit_ch / n_lrn_q, na.rm = TRUE,
         prop_correct_auto_ch = n_correct_auto_ch / lrn_auto, na.rm = TRUE,
         prop_submit_auto_ch = n_submit_auto_ch / lrn_auto, na.rm = TRUE,
         ) %>%
  select(book, release, class_id, student_id, chapter_num,
         n_submit_ch, n_correct_auto_ch, n_submit_auto_ch,
         prop_submit_ch, prop_correct_auto_ch, prop_submit_auto_ch,
         n_submit_ch_plaintext, n_submit_ch_mcq, n_submit_ch_choicematrix,
         n_submit_ch_shorttext, n_submit_ch_clozeassociation, n_submit_ch_association,
         n_submit_ch_imageclozeassociation, n_submit_ch_sortlist, n_submit_ch_formulaV2
         ) %>%
  distinct()

```

Sanity check, the proportion variables should not be greater than 1.

```{r}
favstats(~ prop_submit_ch, data = student_ch_lrn)
favstats(~ prop_correct_auto_ch, data = student_ch_lrn)
favstats(~ prop_submit_auto_ch, data = student_ch_lrn)
```

```{r}

#save(student_ch_lrn, file = "../level-chapter/student_ch_lrn.Rdata", compress = "xz", compression_level = 9)

```

Remove temporary data frames.

```{r}

rm(student_page_auto, student_page_submit, student_page_type,
   responses_auto, responses_lrn, lrn_types, lrn_types_auto)

```

